---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

## get_outputs = function(manifest) {
##   files = sapply(manifest, function(x) x$file)
##   comments = sapply(manifest, function(x) x$comment)
##   sizes = file.size(dest_files)
##   url=sprintf('<a href="%s">%s</a>', dest_files, files)
##   table = cbind(files, comments, sizes, url)
##   table
## }

manifest_df = copy_manifest_files(root, manifest,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(manifest_df)
```

# Summary

The R scripts provided by the authors were used to generate the main
findings in the papers (tables and figures).  All the main findings in
the paper could be reproduced.  Only one model figure (Extended data
Figure 5) was not reproduced simply because the code was not available
in the repository at the time of checking.  However, this omission is
minor.  (NB: the results were checked against the "Accelerated Article
Preview" version of the paper from 8th June 2020, rather than the
final version of the article.)  Overall, this was a straightforward
reproduction, given the diligent documentation and supporting
information describing the environment required to run the code.


\clearpage

# CODECHECKER notes


The github repository was cloned, and renamed to "covid19model-nature"
(as there are two sets of papers in the one repository).

The programs were written in R and required a large number of
dependencies, all of which were available.  I created the following
`codecheck-installs.R` script based on the contents of the
`environment.yml`:

```{r, code = readLines("codecheck-installs.R"), eval=FALSE}
```

The code was first run using the Dockerfile, although this ran the
base model, rather than the analysis for the Nature manuscript.  The
simulations were thus run by running the simulation directly on a
workstation:

```{sh, eval=FALSE}
Rscript base-nature.r --full
```

The run took about 6 hours rather than the anticipated 3 hours, due to
one chain taking much longer to sample from.

Figures required no further post-processing after the R scripts were
run, so these match the layout in the manuscript.  The tables however
required some simple formatting, as the outputs were provided in the
form of CSV files.  (Extended data table 1 was made by merging several
data files, each column coming from a different CSV.  The first column
of extended data table 1 was missing.)

Given that the analysis in this paper is stochastic, and the random
number seed was not fixed, the results in the paper and this run
should not match exactly.  There is very good agreement between the
runs reported in the manuscript and those that were performed here.
 
\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:5,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[3, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[4, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[5, "dest"])
```

```{r,results='asis',echo=FALSE}
df = read.csv(manifest_df[6, "dest"],nrows=11)
Country = df$countries
Percent_Infected = df$text
tab1 = data.frame(Country, Percent_Infected)
tab1 = tab1[order(tab1$Country),]
print(xtable(tab1, caption=manifest_df[6, "comment"]),
      comment=FALSE,
      include.rownames=FALSE)
```

\clearpage


```{r, echo=FALSE, fig.cap=manifest_df[7:13,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[7, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[8, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[9, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[10, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[11, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[12, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[13, "dest"])
```


\clearpage

```{r,results='asis',echo=FALSE}
model_df = read.csv(manifest_df[14, "dest"],nrows=12)
null_df = read.csv(manifest_df[15, "dest"],nrows=12)
averted_df = read.csv(manifest_df[16, "dest"],nrows=12)

Country = model_df$countries
model = model_df$text
null = null_df$text
averted = averted_df$text
etab1 = data.frame(Country, model, null, averted)
etab1 = etab1[order(etab1$Country),]
## swap the UK and Total columns.
uk.row = which(etab1$Country=="United_Kingdom")
total.row = which(etab1$Country=="Total")
etab1[total.row,1] = "All"  ## renamed from Total
temp_row = etab1[uk.row,]
etab1[uk.row,] = etab1[total.row,]
etab1[total.row,] = temp_row

print(xtable(etab1, caption=manifest_df[14, "comment"]),
      comment=FALSE,
      include.rownames=FALSE)
```


\clearpage

# Citing this document

```{r, results='asis', echo=FALSE}
citation(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.

# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
