---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

## get_outputs = function(manifest) {
##   files = sapply(manifest, function(x) x$file)
##   comments = sapply(manifest, function(x) x$comment)
##   sizes = file.size(dest_files)
##   url=sprintf('<a href="%s">%s</a>', dest_files, files)
##   table = cbind(files, comments, sizes, url)
##   table
## }

manifest_df = copy_manifest_files(root, manifest,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(manifest_df)
```

# Summary

WORK IN PROGRESS

This code was (not) straightforward to codecheck.
[... ADD MORE INTERESTING FINDINGS HERE..]

\clearpage

# CODECHECKER notes

The GitHub repo ...
Code was written in ...
I went through the following steps ...
One hard problem was ...

This took ... minutes to complete on {a large workstation, my laptop}.

\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:5,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[3, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[4, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[5, "dest"])
```

```{r,results='asis',echo=FALSE}
df = read.csv(manifest_df[6, "dest"],nrows=11)
Country = df$countries
Percent_Infected = df$text
tab1 = data.frame(Country, Percent_Infected)
tab1 = tab1[order(tab1$Country),]
print(xtable(tab1, caption=manifest_df[6, "comment"]),
      comment=FALSE,
      include.rownames=FALSE)
```

\clearpage


```{r, echo=FALSE, fig.cap=manifest_df[7:13,"comment"]}
# TODO turn into a loop 
knitr::include_graphics(manifest_df[7, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[8, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[9, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[10, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[11, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[12, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[13, "dest"])
```


\clearpage

Extended data table 1 was made by merging several data files, each
column coming from a different CSV.

```{r,results='asis',echo=FALSE}
model_df = read.csv(manifest_df[14, "dest"],nrows=12)
null_df = read.csv(manifest_df[15, "dest"],nrows=12)
averted_df = read.csv(manifest_df[16, "dest"],nrows=12)

Country = model_df$countries
model = model_df$text
null = null_df$text
averted = averted_df$text
etab1 = data.frame(Country, model, null, averted)
etab1 = etab1[order(etab1$Country),]
## swap the UK and Total columns.
uk.row = which(etab1$Country=="United_Kingdom")
total.row = which(etab1$Country=="Total")
etab1[total.row,1] = "All"  ## renamed from Total
temp_row = etab1[uk.row,]
etab1[uk.row,] = etab1[total.row,]
etab1[total.row,] = temp_row

print(xtable(etab1, caption=manifest_df[14, "comment"]),
      comment=FALSE,
      include.rownames=FALSE)
```


\clearpage

# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
